Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-13 analysis/paper/paper.Rmd
Move ref to Fig 1 to results

Model fitness was evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].

@@

>>>>

Model fitness was evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) and posterior fits using `pp_check()` from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].

@@

All models' diagnostic plots indicated good chain mixing and all were deemed suitable for the data by the checking posterior fits (Figure \@ref(fig:posteriors)).
